Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-06 manuscript/main.tex
added `addons.bib` to TeX header
new discussion paragraph

While we did not identify any statistical associations between individual species
and cognitive performance in our youngest subset (0 to 6 months),
it may be because brain developmental trajectories begin \textit{in utero},
and microbial influences (that can only begin at birth)
take additional time to manifest.
Future studies should attempt to link early-life microbial exposures
to future cognitive performance or brain development.

@@

>>>>

@@

While we did not identify any statistical associations between individual species
and cognitive performance in our youngest subset (0 to 6 months),
it may be because brain developmental trajectories begin \textit{in utero},
and microbial influences (that can only begin at birth)
take additional time to manifest.
A prediction experiment aligned to that hypothesis,
targeting future cognitive assessment scores using metagenomes acquired prior to 1 year of age,
revealed a list of most predictive taxa for that task.
The top-ranked species on that list include several 
taxa that were important for predicting concurrent cognitive assessment scores after 18 months, notably
pathobiontic \textit{Enterobacteriaceae} such as
\textit{Escherichia} and \textit{Klebsiella}. 
Representatives of this genus are known to be early and long-term persistent
colonizers of infant intestine that can, in some settings,
promote inflammatory response \cite{popeEnterobacEarlyGut2019}.
Parallel to those species, several tradinionally health-promoting and inflammation-mudulating representatives
of the \textit{Bifidobacterium} genus,
from the early HMO-metabolizer \textit{B. longum} to the
later complex carbohydrate relying \textit{B. pseudocatenulatum} \cite{chungBifidoPsudocatenulatum2021},
commonly associated with weaning to solid food in early age,
have also shown high relative importance.
The involvement of most important taxa in different aspects of inflammatory response
resonate with previous findings that associate chronic inflammation with
changes to neural responses in some types of stimula, notably visual\cite{xieChronicInfNeuro2019}.
